Can BERT learn dialogue specific phenomena? The case of laughter in dialogue act recognition.

### 2020-07-20 reports/Star-SEM Paper/starsem-paper.tex
new title candidate
title and abstract (y)

\title{Tickle me BERT: Using laughter to probe pre-trained encoders for dialogue act recognition}
% TODO rename

@@

\begin{document}
\maketitle
\begin{abstract}
  In this paper, we investigate the usefulness of BERT for dialogue act recognition.
  We are interested in both how useful the pre-training procedure is and 
  how well the model adapts to the dialogue domain.
  To confirm that the fine-tuned model learns to represent dialogical features, 
  we look at how it uses laughter, a phenomenon specific to dialogue.

  % New abstract?
  % In this we investigate whether transformer models can learn to represent phenomena specific to dialogue.
  % Laughter tokens which are not present in BERT pre-trained models can be learned during additional pre-training and fine-tuning on dialogue data. 
  % We use dialogue act recognition as a proxy task and argue that laughter is a useful feature for it.
  % We observe that pre-training and fine-tuning procedures are useful for learning laughter representation, and explore how well the model adapts to the dialogue domain.

\end{abstract}

>>>>

\title{Can BERT learn dialogue specific phenomena? The case of laughter in dialogue act recognition. }

@@

\begin{document}
\maketitle
\begin{abstract}
   In this work we investigate whether transformer models can learn to represent phenomena specific to dialogue.
   Laughter tokens, which are not present in pre-trained BERT models, can be learned during additional pre-training and fine-tuning on dialogue data. 
   We use dialogue act recognition as a proxy task and demonstrate that laughter is a useful feature for it.
   We find that pre-training and fine-tuning procedures are useful for learning laughter representation, and explore how well the model adapts to the dialogue domain.
\end{abstract}
